\bf Approximating Likelihood Ratios with Calibrated Discriminative Classifiers

### 2016-03-16 jasa/paper-jasa.tex
updated legends

\subsection{Diagnostics}

@@

    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig-ratio-dist.pdf}
        \caption{$p( \log \hat r(\hat{s}(\mathbf{x}))) \, | \,\gamma = 0.05)$ }
        \label{fig:decomposed_ratio}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig-likelihood.pdf}
        \caption{$-\log \Lambda(\gamma)$ }
        \label{fig:likelihood}
    \end{subfigure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/fig4.pdf}
    \caption{Observed 5-dimensional data ${\cal D}$ for nominal values $(\alpha=1, \beta=-1)$. The size of ${\cal D}$ is set to $500$.}
    \label{fig:4}
\end{figure}

@@

    \begin{subfigure}[t]{0.43\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/fig5c.pdf}
        \caption{ }
        \label{fig:5c}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.43\textwidth}
        \centering
        \hfill\includegraphics[width=0.9\textwidth]{figures/fig5d.pdf}
        \caption{ }
        \label{fig:5d}
    \end{subfigure}
    \caption{Inference from exact and approximate likelihood ratios. The red dot corresponds
    to the true values $(\alpha=1, \beta=-1)$ used to generate $\mathcal{D}$, the green dot is the MLE
    $(\hat \alpha=1.012, \hat \beta=-0.9221)$  from the exact likelihood, while the blue dot is the MLE $(\hat \alpha=1.008, \hat \beta=-1.004)$ from the approximate likelihood.
    1, 2 and 3-$\sigma$ contours are shown in white.
             (\ref{fig:5a}) The exact log-likelihood for the observed data ${\cal D}$.
             (\ref{fig:5b}) The approximate log-likelihood  evaluated on a coarse $15 \times 15$ fixed grid.
             (\ref{fig:5c}) A Gaussian Process surrogate of the approximate log-likelihood ratio estimated from a Bayesian optimization procedure. White dots show the  parameter points sampled during the optimization process.}
    \label{fig:5}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[height=.9\textheight]{figures/diagnostics.pdf}
    \caption{Diagnostic plots ....}
    \label{fig:ratio_comp}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/likelihood_comp_0.pdf}
        \caption{$-2\log \Lambda(\alpha)$: poorly trained, well calibrated. }
        \label{fig:6a}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ROC_comp0.pdf}
        \caption{ROC: poorly trained, well calibrated. }
        \label{fig:6b}
    \end{subfigure}

    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/likelihood_comp_1.pdf}
        \caption{$-2\log \Lambda(\alpha)$: poorly calibrated, well trained. }
        \label{fig:6c}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ROC_comp1.pdf}
        \caption{ROC: poorly calibrated, well trained. }
        \label{fig:6d}
    \end{subfigure}

    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/likelihood_comp_2.pdf}
        \caption{$-2\log \Lambda(\alpha)$: well trained, well calibrated. }
        \label{fig:6e}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ROC_comp2.pdf}
        \caption{ROC: well trained, well calibrated. }
        \label{fig:6f}
    \end{subfigure}

    \caption{Alternative presentation of Diagnostic plots.}
    \label{fig:diagnostics}
\end{figure}

>>>>

\subsection{Diagnostics}\label{S:diagnostics}

@@

    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig-ratio-dist.pdf}
        \caption{$p( \log \hat r(\hat{s}(\mathbf{x}))) \, | \,\gamma = 0.05)$ }
        \label{fig:decomposed_ratio}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig-likelihood.pdf}
        \caption{$-2\log \Lambda(\gamma)$ }
        \label{fig:likelihood}
    \end{subfigure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/fig4.pdf}
    \caption{Scatter plots for the 500 samples in the 5-dimensional data ${\cal D}$ generated for nominal values $(\alpha=1, \beta=-1)$. }
    \label{fig:4}
\end{figure}

@@

    \begin{subfigure}[t]{0.43\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/fig5c.pdf}
        \caption{ }
        \label{fig:5c}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.43\textwidth}
        \centering
        \hfill\includegraphics[width=0.9\textwidth]{figures/fig5d.pdf}
        \caption{ }
        \label{fig:5d}
    \end{subfigure}
    \caption{Inference from exact and approximate likelihood ratios. The red dot corresponds
    to the true values $(\alpha=1, \beta=-1)$ used to generate $\mathcal{D}$, the green dot is the MLE
     from the exact likelihood, while the blue dot is the MLE  from the approximate likelihood.
    1, 2 and 3-$\sigma$ contours are shown in white.
             (\ref{fig:5a}) The exact $-2\log\Lambda(\alpha,\beta)$ for the observed data ${\cal D}$.
             (\ref{fig:5b}) The approximate $-2\log\Lambda(\alpha,\beta)$ evaluated on a coarse $15 \times 15$  grid.
             (\ref{fig:5c}) A Gaussian Process surrogate of $-2\log\Lambda(\alpha,\beta)$ ratio estimated from a Bayesian optimization procedure. White dots show the  parameter points sampled during the optimization process.}
    \label{fig:5}
\end{figure}

@@

%\begin{figure}
%    \centering
%    \includegraphics[height=.9\textheight]{figures/diagnostics.pdf}
%    \caption{Diagnostic plots ....}
%    \label{fig:ratio_comp}
%\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/likelihood_comp_0.pdf}
        \caption{Poorly trained, well calibrated. }
        \label{fig:6a}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ROC_comp0.pdf}
        \caption{Poorly trained, well calibrated. }
        \label{fig:6b}
    \end{subfigure}

    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/likelihood_comp_1.pdf}
        \caption{Poorly calibrated, well trained. }
        \label{fig:6c}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ROC_comp1.pdf}
        \caption{Poorly calibrated, well trained. }
        \label{fig:6d}
    \end{subfigure}

    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/likelihood_comp_2.pdf}
        \caption{Well trained, well calibrated. }
        \label{fig:6e}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ROC_comp2.pdf}
        \caption{Well trained, well calibrated. }
        \label{fig:6f}
    \end{subfigure}

    \caption{Results from the diagnostics described in Sec.~\ref{S:diagnostics}.  
    The rows correspond to the quality of the training and calibration of the classifier. The left plots probe the sensitivity to $\theta_1$, while the right plots show the ROC curve for a calibrator trained to discriminate samples from $p(\mathbf{x}|\theta_0)$ and samples from $p(\mathbf{x}|\theta_1)$ weighted as indicated in the legend. }

%    \caption{Diagnostic plots for the approximate likelihood ratios. The left plots show slices of $-2\log\Lambda(\alpha,\beta=1)$ for the exact likelihood ratio and the approximate likelihood ratio with different choices of $\theta_1$. The right plots show the ROC curve for a calibrator trained to discriminate samples from $p(\mathbf{x}|\theta_0)$ and samples from $p(\mathbf{x}|\theta_1)$ weighted as indicated in the legend. }
    \label{fig:diagnostics}
\end{figure}
